---
output: github_document
bibliography: inst/add.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# irr2

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/224571371.svg)](https://zenodo.org/badge/latestdoi/224571371)
<!-- badges: end -->

The goal of irr2 is to calculate IRR and NPV. The related functions inspired by @Ellis2019CBA.

## Installation

You can install the released version of irr2 from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("irr2")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JiaxiangBU/irr2")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(irr2)
## basic example code
```

There is a stream of cash flows, down payment with 2200, and next pay back 752.97 each month.
To calcuate the IRR per year.

```{r}
cf1 <- c(-2200, rep(752.9700, 3))
cf1
irr_m <- irr(cf = cf1)
irr_m
((irr_m/100+1)^12-1)*100
```

If the discount rate is 2%, calcuate NPV of this cash flows.
If the discount rate is 1%, calcuate NPV of this cash flows.

```{r}
npv(discount = 2, cf = cf1)
npv(discount = 1.33299, cf = cf1)
npv(discount = 1, cf = cf1)
```

```{r}
irr2 <- irr(c(-100, 39, 59, 55, 20))/100
irr2
-100 +
    39/(1+irr2)^1 +
    59/(1+irr2)^2 +
    55/(1+irr2)^3 +
    20/(1+irr2)^4
```

## Citations

```{r include=FALSE}
citations <- add2pkg::add_zenodo_citation("README.Rmd")
```

```{r echo=FALSE, results='asis'}
cat(citations$Cite)
```

```{r echo=FALSE, results='asis'}
cat(paste0("```BibTex\n",citations$BibTex,"\n```"))
```

```{r echo=FALSE, results='asis'}
cat(citations$Comments)
```

***

`r add2pkg::add_disclaimer("Jiaxiang Li")`

## Reference {-}
